\chapter{Covariance-Domain Dictionary Learning}\label{ch:Cov-DL}
Through this chapter the method covariance domain dictionary learning (Cov-DL) is presented in details. 
Along the presentation of the general method, necessary computational details are derived for the practical solution.
The purpose is to recover the mixing matrix $\mathbf{A}$ from the MMV model, derived in chapter \ref{ch:system_model}, in the under-determined case.   
In the context of compressive sensing the mixing matrix $\mathbf{A}$ in the MMV model is referred to as the dictionary matrix. 
That is the true mixing matrix is estimated as a dictionary matrix, which can take different forms. 
This will be elaborated further in the section of dictionary learning \todo{obs! stemmer dette på tværs a kapitlerne, vi siger A bliver estimeret som en dictionary.}.  

Cov-DL is an algorithm proposed by O. Balkan \cite{Balkan2015}, leveraging the increased dimensionality of the covariance domain. 
The method have shown successful recovering of the mixing matrix $\mathbf{A}$, even in the non-sparse under-determined case with more active sources $k$ than observed measurements $M$, $k \geq M$. 
In short the algorithm consists of three steps. 
First the segmented MMV model of the EEG measurements is transformed into the covariance domain. 
Then, by the increased dimensionality of the covariance domain, it is possible to learn the mixing matrix of the covariance domain, denoted by $\mathbf{D}$, based on the theory of compressive sensing. 
Here two different cases will appear dependent on the relation between the number of sources $N$ and the found dimension of the covariance domain, which of course depends on the number of measurements $M$. 
Lastly, an inverse transformation is performed on the found mixing matrix of the covariance domain $\mathbf{D}$, in order to obtain the wanted mixing matrix $\mathbf{A}$. 
An important aspect of this method is the prior assumption that the sources within one segment are uncorrelated, that is the rows of $\mathbf{X}_s$ being mutually uncorrelated. 
%Notice that the Cov-DL algorithm do only recover the mixing matrix $\mathbf{A}$ given the measurements $\textbf{Y}_s$. Given $\textbf{A}$ the non-segmented source matrix $\mathbf{X}$ is to be recovered by use of the Multiple Sparse Bayesian Learning algorithm, this is described in chapter \ref{ch:M-SBL} 

The section is inspired by chapter 3 in \cite{phd2015} and the article \cite{Balkan2015}. Selected general theory supporting essential parts of the method is elaborated in appendix \ref{app:Cov-DL}.

\input{sections/ch_cov-DL/New_Cov-DL.tex}
%\input{sections/ch_cov-DL/opt_worksheet.tex}