\chapter{Python Scripts}\label{App:code}
The following list and outline contain descriptions of the essential Python scripts which have been used through the implementation, verification and test phases of this thesis. 
\begin{enumerate}
\item \texttt{Data\_Simulation.py}: Contain the functions for simulation of deterministic and stochastic synthetic data, based on manual specification of each system.  
\item \texttt{Data\_EEG.py}: Contain the functions for import of EEG measurements, possible reduction and segmentation.  
\item \texttt{ICA\_Fast.py}: Contain the function to perform ICA.
\item \texttt{Main\_Algorithm.py}: In this script the main algorithm composed by a compilation of the necessary modules. Remark, by letting \texttt{fix = True} Cov-DL is overwritten by $\hat{\mathbf{A}}_{\text{fix}}$. 
\begin{itemize}
\item \texttt{Cov\_DL.py}: Contain the function to perform Cov-DL.
\item \texttt{M\_SBL.py}: Contain the function to perform M-SBL.
\end{itemize} 
\item \texttt{Test\_Synthetic\_data.py}: Compilation of necessary modules to apply the main algorithm to on synthetic data and generate output, cf. chapter \ref{ch:implementation}.
\item \texttt{Test\_EEG.py}: Compilation of necessary modules to apply ICA and the main algorithm on EEG measurements, for the three different cases, cf. section \ref{seg:main_test_description}.  
\item \texttt{Test\_AlphaFrequency.py}: Contain the functions and corresponding compilation to perform alpha wave analysis, cf. section \ref{sec:alpha_test}.
\item \texttt{Test\_k\_Estimation.py}: Contain the functions and corresponding compilation generate estimation of $k$, cf. chapter \ref{ch:estimation_k} 
\end{enumerate}
The Python scripts are all available directly at \url{https://github.com/TrineNyholm/Enclosure_Mattek10b_thesis_2020.git}. Besides the scripts, the folder contains the EEG measurements data base and a folder for which generated figures are allocated.  


	                                                                                                                                                                                                                                                                 
